\documentclass[defaultstyle,11pt]{thesis}

\usepackage{adjustbox}
\usepackage{amsfonts, amsmath, amssymb, amsthm}
\usepackage{booktabs}
% \usepackage[font=small]{caption}
\usepackage[font={small}, textfont=md, skip=.2pt]{caption} % the commented version of this above is the original 
\usepackage{color}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage{filecontents}
\usepackage[draft,inline,nomargin,index]{fixme}
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage{graphicx}		% to insert figures
\PassOptionsToPackage{hyphens}{url}
\usepackage{hyperref}		% PDF hyperreferences??
\usepackage{lastpage}
\usepackage{lmodern}
\usepackage{multicol}
\usepackage{supertabular}
\usepackage{tabularx}
\usepackage[most]{tcolorbox}
\usepackage{textcomp}
\usepackage{tikz}
\usepackage{todonotes}
\usepackage{xspace}

\usepackage{balance,multirow,subcaption,longtable}
\usepackage{makecell,rotating}

\usepackage{xcolor,colortbl}

\usepackage[capitalise,noabbrev,nameinlink]{cleveref}
\newtheorem{theorem}{Theorem}
\newtheorem{cor}[theorem]{Corollary}

\crefformat{footnote}{#2\footnotemark[#1]#3}


\definecolor{darkblue}{rgb}{0.0, 0.0, 0.55}
\hypersetup{
  colorlinks,
  linkcolor=darkblue,
  urlcolor=darkblue,
  citecolor=darkblue,
}



\usepackage[
n,
operators,
advantage,
sets,
adversary,
landau,
probability,
notions,    
logic,
ff,
mm,
primitives,
events,
complexity,
asymptotics,
keys]{cryptocode}

\newcommand{\tabularscale}{0.65}
%%%%%%%%%%%%   All the preamble material:   %%%%%%%%%%%%

\title{Privacy in Centralized Systems}
\author{Theodore Ian}{Martiny}


\advisor{Assistant Professor}				%  #1 {title}
	{Eric Wustrow}			%  #2 {name}

\reader{Dirk Grunwald}		%  2nd person to sign thesis
\readerThree{Sangtae Ha}		%  3rd person to sign thesis
\readerFour{John Black}
\readerFive{Eric Keller}

\degree{Doctor of Philosophy}		%  #1 {long descr.}
	{Ph.D., Computer Science}		%  #2 {short descr.}

\dept{Department of}			%  #1 {designation}
	{Computer Science}		%  #2 {name}

\otherdegrees{B.S., Virginia Commonwealth University, 2012 \\
	      M.S., University of Pittsburgh, 2015 \\
		  M.S., University of Colorado, 2017}


\abstract{  \OnePageChapter	% because it is very short

	The vast majority of online services are run using a Centralized
	infrastructure. The Centralized nature of these services allow for the
	convenience of a uniform experience for all clients. This also requires
	users be completely at the whim of the service provider. Companies often
	offer a vague promise of security and privacy of the data collected from
	their users that the Users cannot verify themselves.

	This dissertation works to develop technologies that allow online services
	such as content providers and secure end-to-end encrypted messengers to
	offer their core functionality with minimal user information allowing
	services \emph{actually} geared towards privacy to provably have client's
	privacy be a core functionality of their service. A service that doesn't
	have access to client data cannot abuse or leak it.

	In order to develop these technologies a fundamental understanding of what
	client information is necessary for the service to function is required.
	This dissertation also examines the DNS system in over 100 countries to
	learn how countries censor access to content at the DNS level and propose
	methodologies to circumvent this violation of citizen privacy.
	
}

\acknowledgements{	\OnePageChapter	% *MUST* BE ONLY ONE PAGE!
	Here's where you acknowledge folks who helped.
	But keep it short, i.e., no more than one page,
	as required by the Grad School Specifications.
}

% \IRBprotocol{E927F29.001X}	% optional!

% \ToCisShort	% use this only for 1-page Table of Contents

% \LoFisShort	% use this only for 1-page Table of Figures
% \emptyLoF	% use this if there is no List of Figures

% \LoTisShort	% use this only for 1-page Table of Tables
% \emptyLoT	% use this if there is no List of Tables

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\input thesis-intro.tex

\input poc.tex
\input signal.tex
\input v4vsv6.tex

%%%%%%%%%   then the Bibliography, if any   %%%%%%%%%
\bibliographystyle{plain}	% or "siam", or "alpha", etc.
\nocite{*}		% list all refs in database, cited or not
\bibliography{refs}		% Bib database in "refs.bib"

% %%%%%%%%%   then the Appendices, if any   %%%%%%%%%
\appendix
\input{signal-stats-proof}
\input{signal-proof}
\input{signal-leveltwodetails}

\input{v4vsv6-appendix}

\end{document}

